Demo: Counterpoint by Construction

### 2019-05-26 doc/farm/farm-abstract.tex
adjust some working

Let us briefly explain how to implement the rule system of 
first-species counterpoint\footnote{The code is available at
\url{https://github.com/halfaya/MusicTools/blob/master/agda/Counterpoint.agda}.}.
In this exercise, we pick a base melody (the \emph{cantus firmus}),
and contruct a counterpoint melody note-by-note in the same rhythm.
The two voices are represented as a list of pitch-interval pairs,
where intervals must not be dissonant ones (2nds, 7ths, or 4ths).

@@

In a counterpoint list, there must not be perfect intervals 
(5ths and octaves) resulted from parallel or similar motion.
Therefore, we define a predicate that checks whether a motion 
is allowed or not.

@@

Now, we can write valid first-species counterpoint as in the 
example below.

>>>>

Let us briefly explain how to implement the rule system of 
first-species counterpoint\footnote{The code is available at
\url{https://github.com/halfaya/MusicTools/blob/master/agda/Counterpoint.agda}.}.
In first-species counterpoint, one starts with a base melody (the \emph{cantus firmus}),
and contructs a counterpoint melody note-by-note in the same rhythm.
The two voices are represented as a list of pitch-interval pairs,
where intervals must not be dissonant (2nds, 7ths, or 4ths).

@@

In addition, it is prohibited to move from any interval to
a perfect interval (5th or octave) via parallel or similar motion.
Therefore, we define a predicate that checks whether a motion 
is allowed or not.

@@

Now we can write valid first-species counterpoint as in the 
example below.
